---
title: "scriptr multi-language test"
format: revealjs
filters:
  - scriptr
---

## R chunk

This chunk should be extracted to `scripts/r/summary.R`.

```{r}
#| filename: scripts/r/summary.R
data <- c(1, 2, 3, 4, 5)

summary(data)
mean(data)
sd(data)
```

## Python chunk

This chunk should be extracted to `scripts/python/hello.py`. `python.reticulate:
false` runs it via the plain system `python` interpreter instead of R's
reticulate package, since this document already uses knitr (for the R chunk
above) as its master engine.

```{python}
#| filename: scripts/python/hello.py
#| python.reticulate: false
def greet(name):
    return f"Hello, {name}"

print(greet("class"))
```

## SQL chunk

This chunk should be extracted to `scripts/sql/query.sql`. SQL cell options
use the `--|` comment prefix instead of `#|`.

```{sql}
--| filename: scripts/sql/query.sql
--| eval: false
SELECT name, count(*) AS n
FROM students
GROUP BY name
ORDER BY n DESC;
```

## Bash chunk

This chunk should be extracted to `scripts/bash/hello.sh`.

```{bash}
#| filename: scripts/bash/hello.sh
echo "hello"
echo "world"
```

## Observable JS chunk

This chunk should be extracted to `scripts/ojs/data.js`. Observable JS is a
Quarto-native engine (it runs in the bundled Deno/browser runtime, with no
external interpreter), and its cell options use the `//|` comment prefix
instead of `#|`, since JavaScript comments start with `//`.

```{ojs}
//| filename: scripts/ojs/data.js
data = [1, 2, 3, 4, 5]

mean = d3.mean(data)
```

## Control case: untagged chunks

None of these should be extracted anywhere.

```{r}
1 + 1
```

```{python}
#| python.reticulate: false
print("not tagged")
```

```{sql}
--| eval: false
SELECT 1;
```

```{bash}
echo "not tagged"
```

```{ojs}
1 + 1
```
