---
title: "scriptr test document"
filters:
  - scriptr
---

## Week 1: Hello World

This chunk should be extracted to `scripts/week1/hello.R`.

```{r}
#| filename: scripts/week1/hello.R
print("Hello, world!")
```

## Week 1: A second script in the same folder

This chunk should be extracted to `scripts/week1/greet.R`.

```{r}
#| filename: scripts/week1/greet.R
greet <- function(name) {
  paste("Hello,", name)
}

greet("class")
```

## Week 2: Nested path

This chunk should be extracted to `scripts/week2/analysis/summary.R`, exercising
creation of multiple nested directories.

```{r}
#| filename: scripts/week2/analysis/summary.R
data <- c(1, 2, 3, 4, 5)

summary(data)
mean(data)
sd(data)
```

## Control case: no filename attribute

This chunk has no `filename` attribute and should NOT be extracted anywhere.

```{r}
x <- 1 + 1
x
```

## Control case: non-R code block

This chunk is not an R block and has no `filename`, so it should be left alone.

```python
print("this is python, not extracted")
```
